gij bent 2

### 2024-12-09 paper/paper.qmd
Add origin of English term CBD
Add more 'tussentaal' references

At the start of the 21^st^ century, it had become clear that Flanders was evolving into a new type of language situation: *diaglossia* [@auer_europe_2005]. In between the dialects and standard language, new language types had appeared, among which so-called "regiolects" (above the dialects) and "regional standards" (below standard language). More generally, however, a new term was coined: *tussentaal*, which roughly translates to "interlanguage". In this article, we will use the term defined by TODO, "Colloquial Belgian Dutch" or CBD.

The new variant CBD is characterised by being hard to define. In general, it is best described as a "standard-adjacent", colloquial form of Belgian Standard Dutch, with both general Flemish elements and region-specific features added to it on all levels (phonology, morphology, syntax etc.). The presence of region-specific features means that CBD is not a monolithic language variety, but rather sounds different across all places in Flanders. This inherent variability is intrinsic to its linguistic identity, but frustrating to linguists, who have been trying to come up with "defining features" for decades [todo citaties Zenner].

>>>>

At the start of the 21^st^ century, it had become clear that Flanders was evolving into a new type of language situation: *diaglossia* [@auer_europe_2005]. In between the dialects and standard language, new language types had appeared, among which so-called "regiolects" (above the dialects) and "regional standards" (below standard language). More generally, however, a new term was coined: *tussentaal*, which roughly translates to "interlanguage". In this article, we will use the English term as defined by @vandekerckhove_cbd_2005: "Colloquial Belgian Dutch" or CBD.

The new variant CBD is characterised by being hard to define. In general, it is best described as a "standard-adjacent", colloquial form of Belgian Standard Dutch, with both general Flemish elements and region-specific features added to it on all levels (phonology, morphology, syntax etc.). The presence of region-specific features means that CBD is not a monolithic language variety, but rather sounds different across all places in Flanders. This inherent variability is intrinsic to its linguistic identity, but frustrating to linguists, who have been trying to come up with "defining features" for decades [i.e. @geeraerts_een_2000;@taeldeman_zich_2008].
